Type theory in type theory with single substitutions

### 2024-09-17 types_2024_postproc/p.tex
meta

Our metatheory in which this paper is
written is thus type theory, some sections are formalised in Agda.

As Agda does not support them directly, we postulate their
constructors and induction principle and add the computation rules
using rewrite rules \cite{DBLP:conf/types/Cockx19}.

Notation and formalisation techniques, including congruence rules.

Prop.

We mainly work in ETT.

>>>>

Our metatheory is observational type theory
\cite{DBLP:phd/hal/Pujet22} with quotient inductive-inductive types
(QIITs). On paper we usually omit writing coercions, so our notation
is close to extensional type theory. Sections \ref{sec:tt} and
\ref{sec:admissible} of this paper are formalised in the proof
assistant Agda, we use a strict Prop-valued
\cite{DBLP:journals/pacmpl/GilbertCST19} equality type with postulated
coercion rule (transport rule) and postulated QIITs with computation
rules added using rewrite rules
\cite{DBLP:journals/pacmpl/CockxTW21}. Our notation on paper is close
to Agda's, we write $\Pi$ types as $(x:A)\ra B$, $\Sigma$ types as
$(x:A)\times B$, and use implicit arguments and overloading
extensively.
